Meta-analysis

### 2019-09-14 01_Meta-analysis_experiments.Rmd
Spelling and grammar corrections, also fungicide AI

* 2015  
   + Hermitage  
   + Dalby - Site abandoned due it insuficient/late disease infection  
   + Emerald

@@

* 2017  
   + Fogerty  
   + Hermitage

@@

**2001 - 2004 trials**  
Trial data were obtained from a non-published manuscript.  
Ratings for powdery Mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc".  
Comparing Trials which have not used the same rating scale wil be done using a percentage change.

**2013 Field trials**  
Fungicide treatments were described in reports in Two letter acronyms. The following is the assumed usage.

```{r}
knitr::kable(
   cbind(Acronym = c("SF", "Ti", "AX", "Ca"),
         Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
         Active_Ingredient = c("Sulphur", "Propiconazole", "Amistar", "Carbendazim")
   )
)
```

>>>>

* 2015  
   + Hermitage  
   + Dalby - Site abandoned due to insufficient/late disease infection  
   + Emerald

@@

* 2017  
   + Missen Flats (Fogerty's farm)  
   + Hermitage

@@

**2001 - 2004 trials**  
Trial data were obtained from a non-published manuscript. 
Ratings for powdery mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc". 
Comparing trials which have not used the same rating scale will be done using a percentage change.

**2013 Field trials**  
Fungicide treatments were described in reports in two letter acronyms.
The following is the assumed usage.

```{r}
knitr::kable(
   cbind(Acronym = c("SF", "Ti", "AX", "Ca"),
         Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
         Active_Ingredient = c("Sulphur", "Propiconazole", "Azoxystrobin and Cyproconazole", "Carbendazim")
   )
)
```
